<br>

```{r echo=FALSE, eval=TRUE, comment=NA, warning=FALSE,error=FALSE, message=FALSE, prompt=FALSE}
#load packages from helpers.R
  source("helpers.R")
```


```{r eval=TRUE, echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis',fig.align='center', fig=TRUE}
DataSet<-read.csv("RTE - clean data 2012-2014 15-1-16.csv", header=TRUE)
# create vectors with year, month, and day
DataSet$Year = Year(as.Date(DataSet$Date,format='%m/%d/%Y'))
DataSet$Month = Month(as.Date(DataSet$Date,format='%m/%d/%Y'))
DataSet$Day = Day(as.Date(DataSet$Date,format='%m/%d/%Y'))
#Hour = Hour(as.Date(DataSet$Date,format='%m/%d/%Y'))
```

The file has the following structure. It has `r nrow(DataSet)` rows and `r ncol(DataSet)` columns.


###Part II: Evolution of energy mix


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
energyMixYear <-  group_by(DataSet, Year) %>% summarise(Fuel = sum(Fuel/4/1000), Coal = sum(Coal/4/1000), Gas = sum(Gas/4/1000),Nuclear = sum(Nuclear/4/1000), Wind = sum(Wind/4/1000), Solar = sum(Solar/4/1000), NetHydro = sum(Hydro/4/1000)+sum(Pumping/4/1000), Bioenergy = sum(Bioenergy/4/1000))


#storing the dataframe
energyMixYear_original = energyMixYear


#re-arranging the dataframe so that it fits the Google Pie Chart and Table format
rownames(energyMixYear)=energyMixYear$Year
energyMixYear$Year = NULL
energyMixYear=as.data.frame(round(t(energyMixYear),0))
energyMixYear$Source=rownames(energyMixYear)
energyMixYear = energyMixYear[,c(4,1,2,3)]
energyMixYear = energyMixYear[order(-energyMixYear$`2014`),]

energyTotals = apply(energyMixYear[,2:ncol(energyMixYear)], 2, sum)

```


<br>

Out of the `r format(energyTotals[ncol(energyMixYear)-1],big.mark=",",scientific=FALSE)` GWh produced on the French soil in `r energyMixYear[nrow(energyMixYear),1]`, the main energy source was `r energyMixYear$Source[1]` with `r energyMixYear[1,ncol(energyMixYear)]/energyTotals[ncol(energyMixYear)-1]*100`%.

<br>

The following table shows the annual energy production broken down by energy sources.

<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
table = gvisTable(energyMixYear)
print(table, 'chart')

Pie2014 <- gvisPieChart(energyMixYear[,c(1,4)], options = list( title='2014 Energy Mix', height = 1000, width = 1000))
#plot(Pie2014)
print(Pie2014, 'chart')
```


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#conversion to String required to use vector as x-axis in Google Charts
#energyMixYear$Year=as.character(energyMixYear$Year)

#print(gvisSteppedAreaChart(energyMixYear, xvar = "Year", yvar = c("Pumping", "Nuclear","Hydro",  "Fuel", "Coal", "Gas", "Wind", "Solar", "Bioenergy"), options=list(isStacked=TRUE,width = 1000, height = 500, vAxis="{format:'#,###GWh'}")), 'chart')

#year to year difference of energy sources
energyMixYear = energyMixYear_original
#stores year on year added capacity for each source of energy
temp = diff(as.matrix(energyMixYear[,2:ncol(energyMixYear)]))
#calculate percentage increase in each source of energy
energyMixYearIncrease = temp / energyMixYear[1:nrow(energyMixYear)-1,2:ncol(energyMixYear)]
colnames(energyMixYearIncrease)=colnames(energyMixYear[,2:ncol(energyMixYear)])


#need to make period calculation automatic
energyMixYearIncrease$Period= c("2012-2013", "2013-2014")

added_energy = round(as.data.frame(t(temp)),0)
added_energy$Source = rownames(added_energy)
added_energy = added_energy[,c(3,1,2)]
colnames(added_energy)[2:ncol(added_energy)]= c("2012-2013", "2013-2014")

m1 = gvisTable(added_energy,options=list(width=600, height=min(400,27*(nrow(added_energy)+1)),allowHTML=TRUE,page='disable'))
print(m1,'chart')
#plot(m1)
```

