
```{r echo=FALSE, eval=TRUE, comment=NA, warning=FALSE,error=FALSE, message=FALSE, prompt=FALSE}
#load packages from helpers.R
  source("helpers.R")
```


```{r eval=TRUE, echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis',fig.align='center', fig=TRUE}
DataSet<-read.csv("RTE - clean data 2012-2014 15-1-16.csv", header=TRUE)
Consumption<-DataSet$Consumption
Forecast<-DataSet$Forecast
Difference<-Forecast - Consumption
Date<-DataSet$Date
max_day_coor<-which.max(Consumption)+1
max_day<-Date[max_day_coor]
```
The file has the following structure. It has `r nrow(DataSet)` rows and `r ncol(DataSet)` columns.<br>

The maximum consumption at one point in time in France between 2012 and 2014 was `r max(Consumption, na.rm = TRUE)` MW.

This is located on row `r which.max(Consumption)+1` and happened on `r max_day`

This is lower than the electrical available power which amounts to 129 310 MW as of 12/31/15.

`r print(gvisLineChart(DataSet, xvar ="Date", yvar = "Consumption"),'chart')`
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}

#data below works be superpatient
print(gvisLineChart(DataSet, xvar = "Date", yvar = c("Consumption"), options=list(isStacked=TRUE,width = 1000, height = 500)), 'chart')
```

We want to see the correlation between the forecast and the consumption. We can conclude that the forecast is of high quality.

We also wanted to compare over the last 6 month the difference between forecast and the consumption. We started by defining the appropriate dataset.

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}

#data below works be superpatient
print(gvisLineChart(DataSet, xvar = "Date", yvar = c("Difference"), options=list(isStacked=TRUE,width = 1000, height = 500)), 'chart')
```
