---
title: "Team project"
author: "Alex, Gaojun, Sergey, Bastien"
output: html_document
---

<br>

```{r echo=FALSE, eval=TRUE, comment=NA, warning=FALSE,error=FALSE, message=FALSE, prompt=FALSE}
#load packages from helpers.R
  source("helpers.R")
```

###Background
We have performed analysis of electricity data provided by the French Distribution Network (RTE)

####Analysis
1. Comparison between supply and demand
2. Evolution of energy mix
3. Correlation between time of the day and solar energy production 
4. Correlation between time of the day and wind energy
5. Correlation between supply and demand vs. import/export
6. Correlation between consumption and weather

####Source

Open data: https://www.data.gouv.fr/fr/datasets/electricite-consommation-production-co2-et-echanges/


```{r child = "RTEAnalytics-Bastien-01.Rmd"}
```

###Part X: High level comments on electricity in France
Over the last three years, the highest consumption point at one single point in time amounted to `r max(Consumption)` MegaWatts. The lowest consumption point at one single point in time amounted to `r min(Consumption)`. The highest consumption point of consumption occurred on 

###Part X: Comparison between supply and demand

`r n<-16`
I am a `r n`J
```{r child = "RTEAnalytics-Alex-01.Rmd"}
```

###Part II: Evolution of energy mix




####??

###Part III: Correlation between time of the day and solar energy production

####??

###Part IV: Correlation between time of the day and wind energy

####Sergey's part

###Part V: Correlation between supply and demand vs. import/export

```{r eval=TRUE, echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis',fig.align='center', fig=TRUE}
DataSet<-read.csv("RTE - clean data 2012-2014 15-1-16.csv", header=TRUE)
```

# create vectors with year, month, and day
DataSet$Year = Year(as.Date(DataSet$Date,format='%m/%d/%Y'))
DataSet$Month = Month(as.Date(DataSet$Date,format='%m/%d/%Y'))
DataSet$Day = Day(as.Date(DataSet$Date,format='%m/%d/%Y'))
Hour = Hour(as.Date(DataSet$Date,format='%m/%d/%Y'))

###plot consumption per day
supply_data = DataSet$Consumption

date_data = sort(DataSet$Date, decreasing = FALSE, index.return = TRUE)
plot(date_data, supply_data)   
#need to re-sequence date

#average monthly consumption
consumption_month <- group_by(DataSet, Month) %>% summarise(consumption = sum(Consumption)/3)
plot(consumption_month, xlab="Month", ylab="Monthly consumption (MWH") 

#annual consumption
consumption_year <- group_by(DataSet, Year) %>% summarise(consumption = sum(Consumption))
plot(consumption_year, xlab="Year", ylab="Annual consumption (MWH)")





###correlation between consumption and forecast
forecast_D_1 = DataSet[,6]               ###DataSet$"Forecast D-1"
forecast_D = DataSete[,7]               ###DataSet$"Forecast D"
c1 <- cbind(DataSet$Consumption, DataSet[,6], DataSet[,7])
cor_consumption <- cor(c1)     ###correlation between consumption and forecast

###import/export
c2 <- sum(as.numeric(DataSet[,19]), as.numeric(DataSet[,20]), as.numeric(DataSet[,21]), as.numeric(DataSet[,22]), as.numeric(DataSet[,23])
plot(date_data, c2)

###Part VI: Correlation between consumption and weather


