<br>

```{r echo=FALSE, eval=TRUE, comment=NA, warning=FALSE,error=FALSE, message=FALSE, prompt=FALSE}
#load packages from helpers.R
  source("helpers.R")
```


```{r eval=TRUE, echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis',fig.align='center', fig=TRUE}
DataSet<-read.csv("RTE - clean data 2012-2014 15-1-16.csv", header=TRUE)
# create vectors with year, month, and day
DataSet$Year = Year(as.Date(DataSet$Date,format='%m/%d/%Y'))
DataSet$Month = Month(as.Date(DataSet$Date,format='%m/%d/%Y'))
DataSet$Day = Day(as.Date(DataSet$Date,format='%m/%d/%Y'))
#Hour = Hour(as.Date(DataSet$Date,format='%m/%d/%Y'))
```


###Part II: Evolution of energy mix


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
energyMixYear <-  group_by(DataSet, Year) %>% summarise(Fuel = sum(Fuel/4/1000), Coal = sum(Coal/4/1000), Gas = sum(Gas/4/1000),Nuclear = sum(Nuclear/4/1000), Wind = sum(Wind/4/1000), Solar = sum(Solar/4/1000), NetHydro = sum(Hydro/4/1000)+sum(Pumping/4/1000), Bioenergy = sum(Bioenergy/4/1000))


#storing the dataframe
energyMixYear_original = energyMixYear


#re-arranging the dataframe so that it fits the Google Pie Chart and Table format
rownames(energyMixYear)=energyMixYear$Year
energyMixYear$Year = NULL
energyMixYear=as.data.frame(round(t(energyMixYear),0))
energyMixYear$Source=rownames(energyMixYear)
energyMixYear = energyMixYear[,c(4,1,2,3)]
energyMixYear = energyMixYear[order(-energyMixYear$`2014`),]
energyTotals = apply(energyMixYear[,2:ncol(energyMixYear)], 2, sum)
```


<br>

The main source of energy production in `r colnames(energyMixYear)[ncol(energyMixYear)]` was `r energyMixYear$Source[1]` with `r round(energyMixYear[1,ncol(energyMixYear)]/energyTotals[ncol(energyMixYear)-1]*100,1)`% of the `r format(energyTotals[ncol(energyMixYear)-1],big.mark=",",scientific=FALSE)` GWh produced on the French soil.

<br>

The following table shows the annual energy production broken down by energy sources, in GWh per year.

<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#need to format numbers
table = gvisTable(energyMixYear)
print(table, 'chart')
```

<br>

The following chart shows the share of each energy source in the production mix in `r colnames(energyMixYear)[ncol(energyMixYear)]`.

<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
Pie2014 <- gvisPieChart(energyMixYear[,c(1,4)], options = list( title='2014 Energy Mix', height = 400, width = 1000))
#plot(Pie2014)
print(Pie2014, 'chart')
```

<br>

The following table shows the increase in energy production for each energy source:

<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#year to year difference of energy sources
energyMixYear = energyMixYear_original
#stores year on year added capacity for each source of energy
temp = diff(as.matrix(energyMixYear[,2:ncol(energyMixYear)]))
#calculate percentage increase in each source of energy
temp = temp / energyMixYear[1:nrow(energyMixYear)-1,2:ncol(energyMixYear)]
colnames(temp)=colnames(energyMixYear[,2:ncol(energyMixYear)])


#need to make period calculation automatic
#energyMixYearIncrease$Period= c("2012-2013", "2013-2014")

added_energy = round(as.data.frame(t(temp)),3)

colnames(added_energy)[1:ncol(added_energy)]= c("2012-2013", "2013-2014")
added_energy$Source = rownames(added_energy)
added_energy = added_energy[,c(3,1,2)]


m1 = gvisTable(added_energy,options=list(width=600, height=min(400,27*(nrow(added_energy)+1)),allowHTML=TRUE,page='disable'), formats=list('2012-2013'='#.#%', '2013-2014'='#.#%'))
print(m1,'chart')
plot(m1)
```

