---
title: "Team project"
author: "Alex, Goajun, Sergey, Bastien"
output: html_document
---

<br>

```{r echo=FALSE, eval=TRUE, comment=NA, warning=FALSE,error=FALSE, message=FALSE, prompt=FALSE}
#load packages from helpers.R
  source("helpers.R")
```

###Background
We have performed analysis of electricity data provided by the French Distribution Network (RTE)

####Analysis
1. Background on electricity in France
2. Evolution of energy mix
3. Correlation studies

####Source

Open data: https://www.data.gouv.fr/fr/datasets/electricite-consommation-production-co2-et-echanges/


```{r child = "RTEAnalytics-Bastien-01.Rmd"}
```

###Part 1: Background on electricity in France
Over the last three years, the highest consumption point at one single point in time amounted to `r max(Consumption)` MegaWatts. The lowest consumption point at one single point in time amounted to `r min(Consumption)`. The highest consumption point of consumption occurred on 

```{r child = "RTEAnalytics-Bastien-02.Rmd"}
```

```{r child = "RTEAnalytics-Alex-01.Rmd"}
```

###Part 3: Correlation studies

####Sergey's part

```{r child = "RTEAnalytics-Sergey-01.Rmd"}
```

###Conclusion
We have becomre more familiar with R by using the set of data. We have confirmed seveal of our assumptions by querying the set of data including:
- the balance of the energy over the period under study
- the evolution of the mix of energy over the period under study
- various sets of correlation